Using Altruistic Peers to Help With Free Web Downloads

### 2008-04-29 docs/abstract/abstract.tex
Create the Kile project for the SIGCOMM poster abstract.

\title{Using Altruistic Peers to Help With Free Web Downloads}
\author{\IEEEauthorblockN{Cameron Dale}
\IEEEauthorblockA{School of Computing Science\\
Simon Fraser University\\
Burnaby, British Columbia, Canada\\
Email: camerond@cs.sfu.ca}}

@@

\begin{abstract}
A large amount of free content is available over the Internet from
many different distributors. Most of this content uses the traditional
client-server model to handle requests from users. However, there is an
opportunity to use peer-to-peer techniques to reduce the cost of
much of this distribution, especially due to the altruistic nature
of many of these users. We present a general technique for
satisfying the needs of this P2P distribution, which is applicable
to many of these distributors systems. Our method makes use of a DHT
for storing the location of peers, using the cryptographic hash of
the file as a key. We then go further and implement a solution for
the distribution of Debian software packages.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%  Section  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{intro}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%  Section  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Related Work}
\label{related}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%  Section  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Situation}
\label{situation}

@@

\subsection{Examples}
\label{examples}

@@

\subsection{Similarities}
\label{similarities}

The important things to note for each of the systems mentioned in
section \ref{examples}, is that they all have the following in
common:
\begin{itemize}
 \item The content is avaliable for anyone to freely download.
 \item The content is divided into distinct units (packages), each of which contains
       a small independent part of all the content.
 \item Users are typically not interested in downloading all of the content
       available.
 \item Hashes of the content and its size are available before the
       download is attempted.
 \item Requests for the content are sent by a tool, not directly by
       the user (though the tool is responding to requests from the user).
\end{itemize}

@@

\subsection{Differences}
\label{differences}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%  Section  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Opportunity}
\label{opportunity}

The situation described in section \ref{situation} presents a clear
opportunity to use some form of peer-to-peer file-sharing protocol.
This sparse interest in a large number of packages, and constant
updating, is well suited to the functionality provided by a
Distributed Hash Table (DHT). DHTs require unique keys to store and
retrieve strings of data, for which the cryptographic hashes used by
these package management systems are perfect for. The stored and
retrieved strings can then be pointers to the peers that have the
content package that hashes to that key. A downloading peer can
lookup the package hash in the DHT and, if it is found,
download the file from those peers and verify the content. If the
package hash can not be found in the DHT, the peer will fallback to
downloading from the original content location (i.e. the network of
mirrors), and once complete will add a new entry to the DHT
indicating that it has the content.

\subsection{Implementation Options}
\label{imp_options}

@@

\subsection{Downloading From Peers}
\label{downloading}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%  Section  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Sample Implementation}
\label{implementation}

A sample implementation has been created that functions as described
in section \ref{opportunity}. This software, called
\texttt{apt-p2p}, interacts with the \texttt{apt} tool found in most
Debian-based Linux distributions. Apt uses SHA1 hashes to
verify most downloaded files, including the large index files that
contain the hashes of the individual packages. We chose this
distribution system as it is familiar to us, and there are
interesting statistics available for analyzing the popularity of the
software packages \cite{popcon}.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{apt_p2p_simulation-size_CDF.eps}
\caption{The CDF of the size of packages in a Debian system, both
for the actual size and adjusted size based on the popularity of
the package.}
\label{size_CDF}
\end{figure}

Figure \ref{size_CDF} shows the package size of the 22,298 packages
available in Debian in January 2008. We can see that most of the
packages are quite small, and so most will therefore not require
sub-piece information to download. We have chosen a piece
size of 512 kB, which means that 17,515 (78\%) of the packages will
not require this information. There are 3054 packages that will
require 2 to 4 pieces, for which the torrent string can be stored
directly with the package hash in the DHT. There are 1667 packages
that will require a separate lookup in the DHT for the longer
torrent string as they require 5 to 70 pieces. Finally, there are
only 62 packages that require more than 70 pieces, and so will
require a separate request to a peer for the torrent string.

\subsection{Current Status}
\label{status}

@@

However, the current implementation does not use the sub-piece
hashing described in section \ref{downloading}, or any parallelizing
of downloads. Instead, it currently chooses a peer at random from
the list of possible peers, and downloads the entire file from that
peer, regardless of the size of the file. This needs to change if
both a) the file is large (more than 512 KB), and b) there are
multiple peers with the file. The storage and retrieval of sub-piece
hashes has not yet been finalized though, and until it is this final
step is not possible.

%%%%%%%%%%%%%%%%%%%%%%%%%%%  Section  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Future Work}
\label{future}

There are some additional steps to be taken to succeed with this
project. First, the storage method of sub-piece hashes needs to be
finalized and properly implemented. The communication built into the
Khashmir-based DHT also needs to be solidified. Some additional peer
statistics data needs to be made available for each peer, so that
some form of analysis is available once the system is deployed. The
reference implementation then needs to be packaged for upload to the
Debian package archive, so that it can benefit from the widest
possible deployment among users.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%  Section  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}
\label{conclusions}

@@

>>>>

\title{Using Altruistic Peers to Help With Free Web Downloads}
\author{\IEEEauthorblockN{Cameron Dale}
\IEEEauthorblockA{School of Computing Science\\
Simon Fraser University\\
Burnaby, British Columbia, Canada\\
Email: camerond@cs.sfu.ca}
\and
\IEEEauthorblockN{Jiangchuan Liu}
\IEEEauthorblockA{School of Computing Science\\
Simon Fraser University\\
Burnaby, British Columbia, Canada\\
Email: jcliu@cs.sfu.ca}}

@@

\begin{abstract}
A large amount of free content is available over the Internet from
many different distributors. Most of this content uses the traditional
client-server model to handle requests from users. However, there is an
opportunity to use peer-to-peer techniques to reduce the cost of
much of this distribution, especially due to the altruistic nature
of many of these users. We present a general technique for
satisfying the needs of this P2P distribution, which is applicable
to many of these distributors systems. Our method makes use of a DHT
for storing the location of peers, using the cryptographic hash of
the file as a key. We then go further and implement a solution for
the distribution of Debian software packages.

@@

@@

@@

@@

The important things to note for each of the systems mentioned
is that they all have the following in
common:
\begin{itemize}
 \item The content is avaliable for anyone to freely download.
 \item The content is divided into distinct units (packages), each of which contains
       a small independent part of all the content.
 \item Users are typically not interested in downloading all of the content
       available.
 \item Hashes of the content and its size are available before the
       download is attempted.
 \item Requests for the content are sent by a tool, not directly by
       the user (though the tool is responding to requests from the user).
\end{itemize}

@@

@@

The situation presents a clear
opportunity to use some form of peer-to-peer file-sharing protocol.
This sparse interest in a large number of packages, and constant
updating, is well suited to the functionality provided by a
Distributed Hash Table (DHT). DHTs require unique keys to store and
retrieve strings of data, for which the cryptographic hashes used by
these package management systems are perfect for. The stored and
retrieved strings can then be pointers to the peers that have the
content package that hashes to that key. A downloading peer can
lookup the package hash in the DHT and, if it is found,
download the file from those peers and verify the content. If the
package hash can not be found in the DHT, the peer will fallback to
downloading from the original content location (i.e. the network of
mirrors), and once complete will add a new entry to the DHT
indicating that it has the content.

@@

@@

A sample implementation has been created that functions as described
previously. This software, called
\texttt{apt-p2p}, interacts with the \texttt{apt} tool found in most
Debian-based Linux distributions. Apt uses SHA1 hashes to
verify most downloaded files, including the large index files that
contain the hashes of the individual packages. We chose this
distribution system as it is familiar to us, and there are
interesting statistics available for analyzing the popularity of the
software packages \cite{popcon}.

@@

Looking at the package size of the 22,298 packages
available in Debian in January 2008. We can see that most of the
packages are quite small, and so most will therefore not require
sub-piece information to download. We have chosen a piece
size of 512 kB, which means that 17,515 (78\%) of the packages will
not require this information. There are 3054 packages that will
require 2 to 4 pieces, for which the torrent string can be stored
directly with the package hash in the DHT. There are 1667 packages
that will require a separate lookup in the DHT for the longer
torrent string as they require 5 to 70 pieces. Finally, there are
only 62 packages that require more than 70 pieces, and so will
require a separate request to a peer for the torrent string.

@@

@@

@@

\end{abstract}
